\Large \textbf{ Phenotype and gene ontology enrichment as guides for disease modeling in \cel{} }

### 2017-08-21 pea_paper_docs/tex/pea.tex
fixed URL in README.md

\documentclass[10pt,letterpaper,twocolumn]{article}
% \usepackage[twocolumn]{geometry}
\usepackage{lmodern}% http://ctan.org/pkg/lm

% use Unicode characters - try changing the option
% if you run into troubles with special characters (e.g. umlauts)
\usepackage[utf8x]{inputenc}
% clean citations
\usepackage{cite}
% hyperref makes references clicky. use \url{www.example.com}
% or \href{www.example.com}{description} to add a clicky url
\usepackage{nameref}
% line numbers
\usepackage[right]{lineno}
% improves typesetting in LaTeX
% \usepackage{microtype}
% degree symbol
\usepackage{gensymb}
\usepackage{amsmath}
\usepackage{booktabs}
% use adjustwidth environment to exceed text width (see examples in text)
\usepackage{changepage}
% adjust caption style
\usepackage[aboveskip=1pt,labelfont=bf,
            labelsep=period,singlelinecheck=off]{caption}
% remove brackets from references
\makeatletter
\renewcommand{\@biblabel}[1]{\quad#1.}
\makeatother

@@

\author{David Angeles-Albores\textsuperscript{1}
\and{}
Raymond YN Lee\textsuperscript{1}
\and{}
Juancarlos Chan\textsuperscript{1}
\and{}
Paul W Sternberg\textsuperscript{1,*}
}

@@

% title goes here:
\twocolumn[
% title
\maketitle

@@

\section*{Abstract}
\bf{}
Genome-wide experiments have the capacity to generate massive amounts of unbiased
data about an organism. In order to interpret this data, dimensionality reduction
techniques are required. One approach is to annotate genes using unified,
unambiguous vocabularies and to test experimental datasets for term enrichment
using probabilistic methods.
Although gene, phenotype and anatomy ontologies exist for \cel{}, no one
software offers enrichment analyses of all three ontologies.
Here, we present the WormBase Enrichment Suite, which offers users the
ability to test all nematode ontologies simultaneously. We show that
the WormBase Enrichment Suite provides valuable insight into different
biological problems, and that phenotype enrichment analysis (PEA) can
help researchers identify disease phenologs, phenotypes that are homologous across
species, which can inform disease modeling in \cel{}. The WormBase Enrichment Suite
analysis can also shed light on RNA-seq datasets by showing what
molecular functions are enriched, which phenotypes these functions are implicated
in and what tissues are overrepresented in the dataset. Finally, we explore the
phenotype-anatomy relationship, showing that a small subset of highly specific
tissues are disproportionately likely to cause an Egl phenotype, but inferring
tissue expression from an Egl phenotype is limited to the largest tissues.
]

@@

\section*{Introduction}
The last decade has seen an explosion of techniques capable of genome-wide
measurements. Some examples of genome-wide tools include
RNA-seq~\cite{Mortazavi2008} to measure gene expression or
CHIP-seq~\cite{Johnson2007} to measure protein binding to chromatin. These tools are capable
of generating large quantities of data. Understanding these data, and generating
hypotheses from them remains challenging. A common approach used to understand
these datasets is to reduce the dimensionality of the data via enrichment
analyses of ontologies~\cite{TheGeneOntologyConsortium2000a}, which helps
researchers understand what terms are
overrepresented beyond random levels. By analyzing overrepresented terms in
aggregate, researchers can better understand what biological processes were most
affected in a given experiment, and form hypotheses about what is
happening~\cite{Rhee2008}.
This approach is limited by what ontologies can be tested for enrichment.
The best-known ontology for biological research is the Gene Ontology (GO), which
provides a controlled language to describe molecular and cellular functions of
genes~\cite{TheGeneOntologyConsortium2000a}.
In \cel{}, gene, tissue and phenotype ontologies exist
% which provide
% controlled languages
with which to describe \cel{} anatomy and phenotypes
respectively~\cite{Schindelman2011,Lee2003}. These ontologies are curated by
professional curators at WormBase, which is a repository of all \cel{}
data~\cite{Howe2016}.
However, enrichment tools
only exist for gene and tissue ontologies
in the community today (see for example~\cite{Chikina2009,Mi2013,Angeles-Albores2016}).
Another limitation is that
tissue enrichment testing is not offered on the same websites as GO enrichment
testing, which requires users to test their data on different websites that may
or may not use different methodologies to detect enrichment.

@@

To facilitate understanding of large datasets, and to make discovery of
phenologs easier, we have completed an enrichment tool suite in WormBase
that allows users to rapidly perform phenotype, tissue and gene ontology
enrichment analyses (PEA, TEA and GEA respectively) on curated \cel{} ontologies
using the same methodology for each one.
% They are located at
% % TODO: include links.
We applied our tools towards the unbiased discovery of phenologues of
multigenic, complex diseases including
% Diseases to study:
systemic lupus erythematosus, obesity and obesity-related traits,  and
rheumatoid arthritis
by using genes associated with these
diseases via genome-wide association studies. We illustrate the utility of
the complete enrichment suite for finding new relationships in complex data by
analyzing a ciliary neuron transcriptome~\cite{Wang2015}. Finally, we show that
the dictionaries generated for these enrichment analyses can help elucidate the
contributions of specific tissues to specific phenotypes.

@@

\begin{figure}[htbp]
  \renewcommand{\familydefault}{\sfdefault}\normalfont{}
  \centering
  \includegraphics[width=\linewidth]{gwas-design.pdf}
  \caption{Experimental design for human-nematode phenologue identification.
           We used GWAS candidates from the EBI-NHGRI catalog to identify
           disease associated genes, then used DIOPT to identify candidate
           orthologs in \cel{}. Orthologs were used to run phenotype, gene
           and tissue ontology enrichment analyses to identify disease
           phenologues.}
\label{fig:gwas}
\end{figure}

@@

\begin{figure}[htbp]
  \renewcommand{\familydefault}{\sfdefault}\normalfont{}
  \centering
  \includegraphics[width=\linewidth]{systemic-lupus.pdf}
  \caption{Phenologue identification for systemic lupus erythematosus.
           \textbf{A} Phenotype Enrichment Analysis. \textbf{B} GO Enrichment
           Analysis. \textbf{C} Lupus in \cel{} may be best represented by
           a combination of three phenotypes: Cell proliferation possibly
           accompanied by aneuploidy; cell fate transformations that may lead
           to dysmorphias; and a molecular phenotype involving impairment of
           the Nonsense-Mediated Decay (NMD) pathway.}
\label{fig:lupus}
\end{figure}

@@

\begin{figure}[htbp]
  \renewcommand{\familydefault}{\sfdefault}\normalfont{}
  \centering
  \includegraphics[width=\linewidth]{ciliary-transcriptome.pdf}
  \caption{PEA shows that the ciliary transcriptome is enriched in phenotypes
  related to cell division. Although this could reflect enrichment of
  microtubules and microtubule-related genes, the enrichment is at least
  partially driven by cell-cycle and DNA repair genes.}
\label{fig:cilia}
\end{figure}

@@

\begin{figure}[htbp]
  \renewcommand{\familydefault}{\sfdefault}\normalfont{}
  \centering
  \includegraphics[width=\linewidth]{Egl-phenotype.pdf}
  \caption{The Egl phenotype is a complex phenotype that is the result of
  interactions between many tissues. To dissect the contributions of individual
  tissues to generating an Egl phenotype, we obtained all genes annotated with
  with an Egl term. \textbf{A} We used TEA on the set of Egl genes to identify
  enriched tissues. \textbf{B} Anatomic diagram showing the tissues that are
  most enriched in the Egl gene set. Color coding shows the qualitative
  ordering of enrichment (red-Most enriched, yellow-least enriched). For clarity,
  not all cells are shown. All vm1 (4 cells) and vm2 (4 cells) muscles are
  symmetrical arranged around the vulva, but only 2 cells are shown for each.
  There are two seam cells on the left and right side of the vulva, but only
  cell on the right is shown. Only terminally differentiated cells are shown.}
\label{fig:egl}
\end{figure}

\subsubsection*{Quantifying the anatomy-phenotype
                mapping via Bayesian probabilities}
Another way to understand the phenotype-anatomy mapping is by considering
how informative a given anatomy term is on a particular phenotype, or vice-versa.
To this end, we calculated two conditional probabilities that helped us answer
this question. The first conditional probability,

\begin{equation}
  P( \text{a gene has Egl annotation} | \text{it is expressed in } X)
\end{equation}

answers the question: For a gene with an expression pattern that includes the
tissue term X (i.e., the gene is expressed at least in X), what is the probability
that this gene has an Egl phenotype (i.e., the phenotype annotations for this
gene include Egl)? For simplicity, we can re-write this equation more succintly
by removing a few words. The calculation of this probability is straightforward
and follows from the definition of conditional probability:

\begin{equation}
  P(\text{Egl}|X) = \frac{N_\text{genes annotated Egl and X}}
                         {N_\text{genes annotated with X}}.
\label{egl_x}
\end{equation}

Equation~\ref{egl_x} measures how likely a gene is to be annotated with an Egl
phenotype given that its expression pattern includes the term $X$. A related
quantity (which is neither the inverse nor the complement) is the conditional
probability that a gene which is annotated with at least the Egl phenotype is
expressed in tissue $X$. That is to say,

\begin{equation}
  P(X|\text{Egl}) = \frac{N_\text{genes annotated Egl and X}}
                         {N_\text{genes annotated with Egl}}.
  \label{x_egl}
\end{equation}

Equation~\ref{x_egl} tells us how probable it is that any given gene that is
annotated with an Egl phenotype includes $X$ as a tissue term. Taken together,
equations~\ref{egl_x} and~\ref{x_egl} help us understand how predictive
anatomic expression is of phenotypes, and how predictive phenotypes are of
anatomic expression.

\begin{table*}
  \renewcommand{\familydefault}{\sfdefault}\normalfont{}
  \centering{}
  \ra{1.3}
  \caption{Conditional probabilities for various tissues. The
  first column shows the conditional probability that a gene has an Egl
  phenotype given that it has expression in tissue $X$ (given by the row).
  The second column shows the conditional probability that a gene has expression
  in the anatomy term X given that it has an Egl phenotype. The first 9 terms
  are the terms for which $P(\text{Egl}|X)$ is maximized. The last three terms
  are the terms which have the highest $P(X|\text{Egl})$. For clarity, the Pn.p
  cells are not shown even though $P(\text{Egl}|\text{Pn.p})\sim 0.24$.}

  \begin{tabular}{@{}lcc@{}}
  \toprule{}
  Tissue & $P(\text{Egl}| X)$ & $P(X|\text{Egl})$\\
  \bottomrule{}\\
  % Data goes here
  P7.pa & $0.30$ & $0.04$\\
  HSN & $0.27$ & $0.11$\\
  vulC & $0.27$ & $0.06$\\
  vulD & $0.26$ & $0.07$\\
  vulE & $0.25$ & $0.06$\\
  vulF & $0.24$ & $0.06$\\
  vulA & $0.24$ & $0.05$\\
  vulB2 & $0.23$ & $0.05$\\
  vulB1 & $0.22$ & $0.05$\\
  nervous system & $0.02$ & $0.72$ \\
  pharynx  & $0.00$ & $0.46$\\
  sex organ & $0.07$ & $0.41$\\
  tail & $0.05$ & $0.33$\\
  \bottomrule{}
  \end{tabular}
\label{tab:cond_probs}
\end{table*}

We calculated the conditional probability that a gene has an Egl phenotype given
that it's expression pattern includes a tissue term $X$ and we searched for the
tissue terms that maximized this probability. The list of terms that maximized this
probability reflected the results from running TEA on the subset of genes that have
an Egl phenotype. We also calculated the conditional probability that a gene has
expression in a tissue term $X$ given that it is annotated with an Egl phenotype
and we searched for terms that maximized this probability (see
Table~\ref{tab:cond_probs}). The terms that maximized this probability were
`nervous system', `pharynx' (a body part with a lot of neurons),
`sex organ' and `tail' (a body part with neurons and hypodermis). In general, the
terms that had a high $P(\text{Egl}|X)$ did not have a high $P(X|\text{Egl})$.
Additionally, the terms that had a high $P(X|\text{Egl})$ are broad terms that
include a lot of cells, whereas the terms that had a high $P(\text{Egl}|X)$
were considerably more specific.
We conclude that the Egl phenotype arises from a small set of tissues. The Egl
phenotype can be best predicted by genes with expression patterns that include
at least one of a small number of cells (mainly vul cells, HSN). On the other
hand, answering whether the expression pattern of a gene includes a particular
anatomic region or tissue given that the gene has an Egl phenotype is hard to
do for small tissues or single cells. However, guesses about what functional system
or broad anatomic region an Egl gene is expressed in can be answered with
confidence ($\sim70\%$ of the time, an Egl mutant is expressed in
the nervous system).

>>>>

\documentclass[10pt, onecolumn]{article}
\usepackage[margin=1in]{geometry}
\usepackage{lmodern}% http://ctan.org/pkg/lm
\usepackage{authblk} % adds affiliations

\usepackage[utf8x]{inputenc}
\usepackage{nameref}
\usepackage[right]{lineno}
\usepackage{amsmath}
\usepackage{booktabs}
\usepackage[numbers,super]{natbib}
\usepackage{changepage}

% adjust caption style
\usepackage[aboveskip=1pt,labelfont=bf,
            labelsep=period,singlelinecheck=off]{caption}
% remove brackets from references
\makeatletter
\renewcommand{\@biblabel}[1]{\quad#1.}
\makeatother

@@

\author[1,2]{David Angeles-Albores}
\author[1]{Raymond Y. N. Lee}
\author[1]{Juancarlos Chan}
\author[1,2,*]{Paul W. Sterberg}
\affil[1]{Division of Biology and Biological Engineering, Caltech,
Pasadena, CA, 91125, USA}
\affil[2]{Howard Hughes Medical Institute, Caltech, Pasadena, CA, 91125, USA}
\renewcommand\Affilfont{\itshape\small{}}

@@

% title goes here:
% title
\maketitle

@@

\section*{Abstract}
\textbf{
Genome-wide experiments have the capacity to generate massive amounts of unbiased
data about an organism. To interpret these data, dimensionality reduction
techniques are required. One approach is to annotate genes using unified,
unambiguous vocabularies and to test experimental datasets for term enrichment
using probabilistic methods.
Although gene, phenotype and anatomy ontologies exist for \cel{}, no one
software offers enrichment analyses of all three ontologies.
Here, we present the WormBase Enrichment Suite, which offers users the
ability to test all nematode ontologies simultaneously. We show that
the WormBase Enrichment Suite provides valuable insight into different
biological problems, and that phenotype enrichment analysis (PEA) can
help researchers identify disease phenologs, phenotypes that are homologous across
species, which can inform disease modeling in \cel{}. The WormBase Enrichment Suite
analysis can also shed light on RNA-seq datasets by showing what
molecular functions are enriched, which phenotypes these functions are implicated
in and what tissues are overrepresented in the dataset. Finally, we explore the
phenotype-anatomy relationship, showing that a small subset of highly specific
tissues are disproportionately likely to cause an Egl phenotype, but inferring
tissue expression from an egg-laying (Egl) phenotype is limited to the largest tissues.
}

\vspace{10mm}

@@

\section*{Introduction}
The last decade has seen an explosion of techniques capable of genome-wide
measurements. Some examples of genome-wide tools include
RNA-seq~\cite{Mortazavi2008} to measure gene expression or
CHIP-seq~\cite{Johnson2007} to measure protein binding to chromatin. These tools
are capable of generating large quantities of data. Understanding these data,
and generating hypotheses from them remains challenging. A common approach used
to understand these datasets is to reduce the dimensionality of the data via
enrichment analyses of ontologies~\cite{TheGeneOntologyConsortium2000a}, which
helps researchers understand what terms are overrepresented beyond random
levels. By analyzing overrepresented terms in aggregate, researchers can better
understand what biological processes were most affected in a given experiment,
and form hypotheses about what is happening~\cite{Rhee2008}. This approach is
limited by what ontologies can be tested for enrichment. The best-known ontologies
for biological research are the Gene Ontologies (GO), which provide a controlled
language to describe the biological, cellular and molecular aspects and functions of
genes~\cite{TheGeneOntologyConsortium2000a}. In \cel{}, gene, tissue and
phenotype ontologies exist with which to describe \cel{} anatomy and phenotypes
respectively~\cite{Schindelman2011,Lee2003}. These latter ontologies are developed by
professional curators at WormBase, which is a repository of \cel{}
data~\cite{Howe2016}. However, enrichment tools currently only exist for gene and tissue
ontologies in the community today (see for
example~\cite{Chikina2009,Mi2013,Angeles-Albores2016}). Another limitation is
that tissue enrichment testing is not offered on the same websites as GO
enrichment testing, which requires users to test their data on different
websites that may or may not use different methodologies to detect enrichment.

@@

To facilitate understanding of large datasets, we have developed the WormBase
Enrichment Suite (URL:\
\url{http://www.wormbase.org/tools/enrichment/tea/tea.cgi}) that allows users to
rapidly perform phenotype, tissue and gene ontology enrichment analyses (PEA,
TEA and GEA respectively) on curated \cel{} ontologies using the same
methodology for each one. As examples of use cases, we applied our tools towards
the unbiased discovery of phenologs of multigenic, complex diseases including
systemic lupus erythematosus, obesity and obesity-related traits, and rheumatoid
arthritis by using genes associated with these diseases via genome-wide
association studies. We illustrate the utility of the complete enrichment suite
for finding new relationships in complex data by analyzing a ciliary neuron
transcriptome~\cite{Wang2015}. Finally, we show that the dictionaries generated
for these enrichment analyses can help elucidate the contributions of specific
tissues to specific phenotypes.

@@

\begin{figure}[htbp]
  \renewcommand{\familydefault}{\sfdefault}\normalfont{}
  \centering
  \includegraphics[width=.5\linewidth]{gwas-design.pdf}
  \caption{Experimental design for human-nematode phenolog identification.
           We used GWAS candidates from the EBI-NHGRI catalog to identify
           disease associated genes, then used DIOPT to identify candidate
           orthologs in \cel{}. Orthologs were used to run phenotype, gene
           and tissue ontology enrichment analyses to identify disease
           phenologs.}
\label{fig:gwas}
\end{figure}

@@

\begin{figure}[htbp]
  \renewcommand{\familydefault}{\sfdefault}\normalfont{}
  \centering
  \includegraphics[width=.5\linewidth]{systemic-lupus.pdf}
  \caption{phenolog identification for systemic lupus erythematosus.
           \textbf{A} Phenotype Enrichment Analysis. \textbf{B} GO Enrichment
           Analysis. \textbf{C} Lupus in \cel{} may be best represented by
           a combination of three phenotypes: Cell proliferation possibly
           accompanied by aneuploidy; cell fate transformations that may lead
           to dysmorphias; and a molecular phenotype involving impairment of
           the Nonsense-Mediated Decay (NMD) pathway.}
\label{fig:lupus}
\end{figure}

@@

\begin{figure}[htbp]
  \renewcommand{\familydefault}{\sfdefault}\normalfont{}
  \centering
  \includegraphics[width=.5\linewidth]{ciliary-transcriptome.pdf}
  \caption{PEA shows that the ciliary transcriptome is enriched in phenotypes
  related to cell division. Although this could reflect enrichment of
  microtubules and microtubule-related genes, the enrichment is at least
  partially driven by cell-cycle and DNA repair genes.}
\label{fig:cilia}
\end{figure}

@@

\begin{figure}[htbp]
  \renewcommand{\familydefault}{\sfdefault}\normalfont{}
  \centering
  \includegraphics[width=.6\linewidth]{Egl-phenotype.pdf}
  \caption{The Egl phenotype is a complex phenotype that is the result of
  interactions between many tissues. To dissect the contributions of individual
  tissues to generating an Egl phenotype, we obtained all genes annotated with
  with an Egl term. \textbf{A} We used TEA on the set of Egl genes to identify
  enriched tissues. \textbf{B} Anatomic diagram showing the tissues that are
  most enriched in the Egl gene set. Color coding shows the qualitative
  ordering of enrichment (red-Most enriched, yellow-least enriched). For clarity,
  not all cells are shown. All vm1 (4 cells) and vm2 (4 cells) muscles are
  symmetrical arranged around the vulva, but only 2 cells are shown for each.
  There are two seam cells on the left and right side of the vulva, but only
  cell on the right is shown. Only terminally differentiated cells are shown.}
\label{fig:egl}
\end{figure}

\subsubsection*{Quantifying the anatomy-phenotype
                mapping via Bayesian probabilities}
Another way to understand the phenotype-anatomy mapping is by considering how
informative a given anatomy term is on a particular phenotype, or vice-versa. To
this end, we calculated two conditional probabilities that helped us answer this
question. The first conditional probability,
\begin{equation}
  P( \text{a gene has Egl annotation} | \text{it is expressed in } X)
\end{equation}
answers the question: For a gene with an expression pattern that includes the
tissue term X (i.e., the gene is expressed at least in X), what is the
probability that this gene has an Egl phenotype (i.e., the phenotype annotations
for this gene include Egl)? For simplicity, we can re-write this equation more
succintly by removing a few words. The calculation of this probability is
straightforward and follows from the definition of conditional probability:
\begin{equation}
  P(\text{Egl}|X) = \frac{N_\text{genes annotated Egl and X}}
                         {N_\text{genes annotated with X}}.
\label{egl_x}
\end{equation}
Equation~\ref{egl_x} measures how likely a gene is to be annotated with an Egl
phenotype given that its expression pattern includes the term $X$. A related
quantity (which is neither the inverse nor the complement) is the conditional
probability that a gene which is annotated with at least the Egl phenotype is
expressed in tissue $X$. That is to say,
\begin{equation}
  P(X|\text{Egl}) = \frac{N_\text{genes annotated Egl and X}}
                         {N_\text{genes annotated with Egl}}.
  \label{x_egl}
\end{equation}
Equation~\ref{x_egl} tells us how probable it is that any given gene that is
annotated with an Egl phenotype includes $X$ as a tissue term. Taken together,
equations~\ref{egl_x} and~\ref{x_egl} help us understand how predictive anatomic
expression is of phenotypes, and how predictive phenotypes are of anatomic
expression.

\begin{table*}
  \renewcommand{\familydefault}{\sfdefault}\normalfont{}
  \centering{}
  \ra{1.3}
  \begin{tabular}{@{}lcc@{}}
  \toprule{}Tissue & $P(\text{Egl}| X)$ & $P(X|\text{Egl})$\\
  \bottomrule{}P7.pa & $0.30$ & $0.04$\\
  HSN & $0.27$ & $0.11$\\
  vulC & $0.27$ & $0.06$\\
  vulD & $0.26$ & $0.07$\\
  vulE & $0.25$ & $0.06$\\
  vulF & $0.24$ & $0.06$\\
  vulA & $0.24$ & $0.05$\\
  vulB2 & $0.23$ & $0.05$\\
  vulB1 & $0.22$ & $0.05$\\
  nervous system & $0.02$ & $0.72$ \\
  pharynx  & $0.00$ & $0.46$\\
  sex organ & $0.07$ & $0.41$\\
  tail & $0.05$ & $0.33$\\
  \bottomrule{}
  \end{tabular}
  \caption{Conditional probabilities for various tissues. The
  first column shows the conditional probability that a gene has an Egl
  phenotype given that it has expression in tissue $X$ (given by the row).
  The second column shows the conditional probability that a gene has expression
  in the anatomy term X given that it has an Egl phenotype. The first 9 terms
  are the terms for which $P(\text{Egl}|X)$ is maximized. The last three terms
  are the terms which have the highest $P(X|\text{Egl})$. For clarity, the Pn.p
  cells are not shown even though $P(\text{Egl}|\text{Pn.p})\sim 0.24$.}
\label{tab:cond_probs}
\end{table*}

We calculated the conditional probability that a gene has an Egl phenotype given
that it's expression pattern includes a tissue term $X$ and we searched for the
tissue terms that maximized this probability. The list of terms that maximized
this probability reflected the results from running TEA on the subset of genes
that have an Egl phenotype. We also calculated the conditional probability that
a gene has expression in a tissue term $X$ given that it is annotated with an
Egl phenotype and we searched for terms that maximized this probability (see
Table~\ref{tab:cond_probs}). The terms that maximized this probability were
`nervous system', `pharynx' (a body part with a lot of neurons), `sex organ' and
`tail' (a body part with neurons and hypodermis). In general, the terms that had
a high $P(\text{Egl}|X)$ did not have a high $P(X|\text{Egl})$. Additionally,
the terms that had a high $P(X|\text{Egl})$ are broad terms that include a lot
of cells, whereas the terms that had a high $P(\text{Egl}|X)$ were considerably
more specific. We conclude that the Egl phenotype arises from a small set of
tissues. The Egl phenotype can be best predicted by genes with expression
patterns that include at least one of a small number of cells (mainly vul cells,
HSN). On the other hand, answering whether the expression pattern of a gene
includes a particular anatomic region or tissue given that the gene has an Egl
phenotype is hard to do for small tissues or single cells. However, guesses
about what functional system or broad anatomic region an Egl gene is expressed
in can be answered with confidence ($\sim70\%$ of the time, an Egl-causing gene
is expressed in the nervous system).
